Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue of Hybrid UAVs and Biped Robots Team System

### 2023-01-06 paper/paperOneCol.tex
IEEE Contributed Version

\title{Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue of Hybrid UAVs and Biped Robots Team System}

\author{Min-Yen Lee and Bor-Sen Chen, \IEEEmembership{Life Fellow, IEEE,}}

\begin{document}
\maketitle

\begin{abstract}
In this study, we integrate a local motion planning and robust $H_\infty$ decentralized feedforward reference tracking fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R). A system architecture of performing S\&R tasks for each agent in URTS is proposed to explain how to integrate reference trajectory planning and tracking control in URTS for S\&R usage. In order to optimally allocate tasks to each agent in URTS, a task allocate problem is investigated. In order to optimally plan a path for each agent in URTS to reach these allocated task locations, a path planning problem is formulated. To deal with complex S\&R terrain, we decompose the path planning problem into three steps, i.e., (i) global path planning, (ii) behavior decision and (iii) local motion planning. Through such decomposition, some roadmap-based path planning algorithms can be applied to the global path planning of agents in URTS. By the behavior decision, we can decide what behavior to follow the global path according to the terrain environment. Next, we focus on the local motion planning problem of flying behavior for UAV and walking behavior for robot, and then the tracking control problem for UAVs and robots in the hybrid team system. The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail. By converting the dynamics models of UAV and robot into an unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is proposed for each agent in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation. Then, the design of the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure. With the help of MATLAB LMI Toolbox, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC design problem of each UAV and robot in URTS is effectively solved. Finally, the simulation results are used to demonstrate the integration of local motion planning with the S\&R tasks of hybrid URTS and to verify the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
\end{abstract}

\maketitle

@@

\subsection{Local Motion Planning}
After a specific behavior $\beta_n\in\mathcal{B}$ is determined, the next step is to plan a motion to achieve the specific behavior. Local motion planning block is like global path planning block but with smaller scale and higher resolution and precision. Collision checking is needed since we consider agent as a point in global path planning block but it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block, i.e., reference path $r[k]$, is also a path (it is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it). The flowchart of local motion planning block is shown in Fig. \ref{fig:LMP}.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{
        (a) The flowchart of Local Motion Planning block in Fig. \ref{fig:sys} of each agent in URTS. Some basic behaviors of UAV and robot mentioned in Fig. \ref{fig:behavior} are given to futher illustrate the flow of this block. The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior decision. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or discrete signal) planned by a specific behavior block. For UAVs, the moving block is described in (b). For robots, the moving block is described in (c). 
        (b) The moving block of each UAV. The flying block in it is described detailly in Fig. \ref{fig:FandW}. 
        (c) The moving block of each robot. The the walking block in it is described detailly in Fig. \ref{fig:FandW}.}
    \label{fig:LMP}
\end{figure*}

To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot. A more detailed description will be given in the next section. $r[k]$ then pass to next block, i.e., reference tracking control block, as shown in Fig. \ref{fig:sys}.

\subsection{Reference Tracking Control}
To analyze the control problem in the continuous time domain, $r[k]$ will be first converted to a continuous signal by D/A convertor with a timescale, i.e., sampling period. By analyzing the dynamic model of each agent, a desired reference trajectory $r(t)$ is planned. $r(t)$ describes the position and orientation that need to be reached over time by a machine system governed by a dynamic equation. Note that the path and trajectory are distinguished in some literature. Different from path (e.g., $(\sigma_n)$ or $r[k]$), a trajectory $r(t)$ has considered the time in physic world. We also distinguish them in this way in this article.

If each agent in hybrid URTS can track each own reference trajectory $r(t)$, then they can move in the physical world as we expect. To this end, a reference tracking control method needs to be designed. It will be discussed detailly in Section IV. In addition, the sensing information collected by the sensors in this block is not only used for control but also sent back to the upper decision as shown in Fig. \ref{fig:sys}.

@@

Now, suppose the UAV flying behavior occurs between time step $k_1$ and $k_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[k_1,k_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[k_1,k_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[k_1,k_2+D(k_2-k_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $[
    x_r[k], y_r[k], z_r[k]
]^T$. Subsequently, we consider the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be planned beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be planned by combining them together, i.e., $r[k] = [
    x_r[k], y_r[k], z_r[k], \phi_r[k]
]^T\in\mathbb{R}^{4}$. The flowchart of flying motion planning is shown in Fig. \ref{fig:FandW} (a).

@@

\subsection{Local motion planning of walking of robot}
By Lagrange equation, the dynamic model of a biped robot in URTS can be formulated as:
\begin{equation} \label{eq:robot} 
    \begin{split}
        & \tau_R = M_R(q)\ddot{q} + C(q,\dot{q})\dot{q} + G(q)    
    \end{split}
\end{equation}
where $\tau_R$ is the total torque on revolute joints, $q,\dot{q},\ddot{q}\in\mathbb{R}^{12}$  are angular position, angular velocity, and angular acceleration vector of revolute joints, $M_R(q)\in\mathbb{R}^{12\times 12}$ is the inertia matrix, $C(q,\dot{q})\in\mathbb{R}^{12}$ is the Coriolis and centripetal force vector and $G(q)\in\mathbb{R}^{12}$ is the gravitational force vector. The detailed kinematic and dynamic parameters can be found in the online source \cite{ourrobot}. For biped robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is planned in the joint space. Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to plan a stable walking pattern to prevent robot from falling. These make the planning of walking motion of robot more difficult. In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to plan the walking motion of each biped robot in URTS.

@@

\textit{
    \begin{remark}
        A frame (or homogeneous transformation) in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame. That is, given the frames of two joints in a link with known kinematics, the frames of joints between them can be found by \textnormal{IK}. Hence, we need to find the position paths and orientation paths, which compose the desired path.
    \end{remark}
}

@@

To plan the CoM postion path $(CP_n)$, ZMP path needs to be planned first. ZMP path can be planned through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path points out when the feet are on the ground. Suppose the CoM height $z_c$ of biped robot is kept constant when walking, then the biped robot model can be regarded as an 3D-LIPM \cite{kajita2001real}:
\begin{equation} \label{eq:LIPM}
    \begin{split}
        & \ddot{x}_c = \frac{g}{z_c}(x_c - p_x) \\
        & \ddot{y}_c = \frac{g}{z_c}(y_c - p_y)
    \end{split}
\end{equation}
where $(x_c, y_c, z_c)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, and $(p_x,p_y)$ is the position of ZMP on the $x$-$y$ plane. Since $z_c$, $g$ and $(p_x,p_y)$ are given, $(x_c, y_c)$ can be solved. From the dynamic equations in the $x$ and $y$ directions in (\ref{eq:LIPM}), it can be found that they are decoupled and thus can be calculated separately. Therefore, only the solution in the $x$ direction is given below (the $y$ direction as the same). To solve it, a method is proposed to convert it to a servo problem \cite{1241826}:
\begin{equation} \label{eq:output tracking}
    \begin{split}
        & \dot{\bar{x}}_c = A\bar{x}_c + Bu_s \\
        & y_s = C\bar{x}_c
    \end{split}
\end{equation}
where $\bar{x}_c = \begin{bmatrix}
    x_c \\ \dot{x}_c \\ \ddot{x}_c
\end{bmatrix}$, $A = \begin{bmatrix}
    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
\end{bmatrix}$, $B = \begin{bmatrix}
    0 \\ 0 \\ 1
\end{bmatrix}$, and $C = \begin{bmatrix}
    1 & 0 & -z_c/g
\end{bmatrix}$. Our goal is to find a control input $u_s$ in order that the output $y_s$ can track the ZMP reference trajectory $p_x$ so that the state $x_c$, i.e., the solution of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path can be planned. Unlike conventional methods, the problem is solved by the optimal control. The system is discretized first and the discrete LQ optimal tracker is employed to achieve the output tracking. The formulation can be found in TABLE 4.4-1 in \cite{lewis2012optimal}. The CoM position path $(CP_n)$ can then be obtained by combining $x_c$ and $y_c$ with $z_c$.

@@

\section{Reference tracking control of each agent in hybrid URTS}
Through the previous step, the planning of the reference path $r[k]$ of each agent in hybrid URTS has been completed. However, in order to calculate the unplannable reference paths, i.e., $\phi_[k]$ and $\theta_r[k]$, of UAV and analyze the reference trajectory tracking problem in the continuous domain, we have to transform $r[k]$ into the reference trajectory $r(t)$. Before converting the planned reference path $r[k]$ to desired reference trajectory $r(t)$, we first convert the UAV dynamic model in (\ref{eq:uav}) and robot dynamic model in (\ref{eq:robot}) into a form called agent dynamic model in a hybrid team to analyze their team formation tracking control problems together. Through some appropriate variable transformations, we have:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
\end{equation}
where $u(t)\in\mathbb{R}^n$ is the control input vector, $x(t)\in\mathbb{R}^n$ is the state vector, $M(x(t))\in\mathbb{R}^{n\times n}$ is the inertia matrix, and $H(x(t),\dot{x}(t))\in\mathbb{R}^n$ is the non-inertial force vector. The control law for an agent in URTS is given as:
\begin{equation} \label{eq:control}
    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
\end{equation}
where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t))$, $\ddot{r}(t)$ and $H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system tracking robustness. For each UAV in hybrid URTS, we have $u(t)=\begin{bmatrix}
    f_u \\ \tau_u
\end{bmatrix}$, $x(t)=\begin{bmatrix}
    X \\ \Theta
\end{bmatrix}$, $M(x(t))=\begin{bmatrix}
    mI & 0 \\ 0 & J
\end{bmatrix}$, $H(x(t),\dot{x}(t))=\begin{bmatrix}
    0 \\ \dot{\Theta}\times(J\dot{\Theta})
\end{bmatrix}+\begin{bmatrix}
    f_g \\ 0
\end{bmatrix}+\begin{bmatrix}
    K_F & 0 \\
    0 & K_\tau
\end{bmatrix}\begin{bmatrix}
    \dot{X} \\ \dot{\Theta}
\end{bmatrix}$, and $n=6$ by UAV dynamics in (\ref{eq:uav}). For each robot in hybrid URTS, we have $u(t)=\tau_R$, $x(t)=q$, $M(x(t))=M_R(q)$, $H(x(t),\dot{x}(t))=C(q,\dot{q})\dot{q} + G(q)$, and $n=12$ by robot dynamics in (\ref{eq:robot}).

\textit{
    \begin{remark}
        The difference between the control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedforward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$. This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be use in control law $u(t)$. While the asymptotical tracking control is achieved, i.e., $x(t)\rightarrow r(t)$, feedforward linearization control will be achieved too.
    \end{remark}
}
To complete the planning of reference trajectory $r(t)$ of each agent, a D/A converter is used to transform the reference path $r[k]$ (output of local motion planning) into a continuous signal $r'(t)$ as shown in Fig. \ref{fig:tracking}. For UAV, we get $r'(t) = [x_r, y_r, z_r, \phi_r]^T\in\mathbb{R}^{4}$. Besides, for an UAV in hybrid URTS, it can be seen that the control input $u(t)=[f_u^T, \tau_u^T]^T = [f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actuator control input $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ for UAV since UAV is an underactuated system. The two degrees of freedom we reserved in Section III-A, i.e., $\phi_r$ and $\theta_r$, are just to solve this problem. By substituting $\Theta=\begin{bmatrix}
    \phi_r \\ \theta_r \\ \psi_r
\end{bmatrix}$ into $\begin{bmatrix}
        f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
        0 \\ 0 \\ F
\end{bmatrix}$ from UAV dynacmis in (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations using inverse dynamic because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given. Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]^T$. At the same time, we find $u'(t)$. For biped robot, we directly have $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system. So far, the transformation between reference path $r[k]$ and reference trajectory $r(t)$ for each agent in hybrid URTS is done. We define the process of converting $r'(t)$ and $u(t)$ into $r(t)$ and $u'(t)$ mentioned above as the reference generation block in Fig. \ref{fig:tracking}.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/tracking.png}\caption{
    (a) The flowchart of Reference Tracking Control block in Fig. \ref{fig:sys} of each agent in hybrid URTS. The controller block is described in (d). The controller block (the proposed general $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system. It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actuator control input $u'(t)\in\mathbb{R}^4$ different for UAV. The reference generator block is introduced to deal with this problem. For UAVs, the reference generator block is described in (b). For robots, the reference generator block is described in (c). 
    (b) The reference generator block for each UAV. $u'(t)$ and $r(t)$ can be calculated from $u(t)$ and $r'(t)$ by inverse dynamic through the UAV dynamic model in (\ref{eq:uav}). 
    (c) The reference generator block for each robot. $u'(t)=u(t)$ and $r(t)=r'(t)$ since the robot dynamic model in (\ref{eq:robot}) is fully actuated. 
    (d) The proposed general $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme for each agent in hybrid URTS.}
    \label{fig:tracking}
\end{figure*}

>>>>

\begin{document}

@@

\subsection{Local Motion Planning}
After a specific behavior $\beta_n\in\mathcal{B}$ is determined, the next step is to plan a motion to achieve the specific behavior. Local motion planning block is like the global path planning block but with smaller scale and higher resolution and precision. Collision checking is needed since we consider agent as a point in the global path planning block but it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block, i.e., reference path $r[k]$, is also a path (it is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it). The flowchart of local motion planning block is shown in Fig. \ref{fig:LMP}.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{
        (a) The flowchart of Local Motion Planning block in Fig. \ref{fig:sys} of each agent in URTS. Some basic behaviors of UAV and robot mentioned in Fig. \ref{fig:behavior} are given to futher illustrate the flow of this block. The corresponding motion planning of an agent will be executed according to the behavior determined by Behavior Decision block. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or discrete signal) planned by a specific behavior block. For UAVs, Moving block is described in (b). For robots, Moving block is described in (c). 
        (b) Moving block of each UAV. Flying block in it is described detailly in Fig. \ref{fig:FandW}. 
        (c) Moving block of each robot. Walking block in it is described detailly in Fig. \ref{fig:FandW}.}
    \label{fig:LMP}
\end{figure*}

To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot. A more detailed description will be given in the next section. $r[k]$ then passes to next block, i.e., Reference Tracking Control block, as shown in Fig. \ref{fig:sys}.

\subsection{Reference Tracking Control}
To analyze the reference tracking control problem in the continuous time domain, the reference path $r[k]$ will be first converted to a continuous signal $r'(t)$ by D/A convertor with a timescale, i.e., sampling period. By analyzing the dynamic model of each agent, a desired reference trajectory $r(t)$ is planned. $r(t)$ describes the position and orientation that need to be reached over time by a machine system governed by a dynamic equation. Note that the path and trajectory are distinguished in some literature. Different from path (e.g., $(\sigma_n)$ or $r[k]$), a trajectory $r(t)$ has considered the time in physic world. We also distinguish them in this way in this article.

If each agent in hybrid URTS can track each own reference trajectory $r(t)$, then they can move in the physical world as we expect. To this end, a reference tracking control method needs to be designed. It will be discussed detailly in Section IV. In addition, the sensing information collected by the sensors in this block is not only used for reference tracking control but also fed back to the high-level block as shown in Fig. \ref{fig:sys}.

@@

Now, suppose the UAV flying behavior occurs between time step $k_1$ and $k_2$, i.e., $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[k_1,k_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[k_1,k_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[k_1,k_2+d(k_2-k_1)], \sigma_n'\in\mathbb{R}^3$, where $d\in\mathbb{Z}$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $[
    x_r[k], y_r[k], z_r[k]
]^T$. Subsequently, we consider the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be planned beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be planned by combining them together, i.e., $r[k] = [
    x_r[k], y_r[k], z_r[k], \phi_r[k]
]^T\in\mathbb{R}^{4}$. The flowchart of flying motion planning is shown in Fig. \ref{fig:FandW} (a).

@@

\subsection{Local motion planning of walking of robot}
By Lagrange equation, the dynamic model of a biped robot in URTS can be formulated as:
\begin{equation} \label{eq:robot} 
    \begin{split}
        & \tau_R = M_R(q)\ddot{q} + C(q,\dot{q})\dot{q} + G(q)    
    \end{split}
\end{equation}
where $\tau_R$ is the total torque on revolute joints, $q,\dot{q},\ddot{q}\in\mathbb{R}^{12}$  are angular position, angular velocity, and angular acceleration vector of revolute joints, $M_R(q)\in\mathbb{R}^{12\times 12}$ is the inertia matrix, $C(q,\dot{q})\in\mathbb{R}^{12}$ is the Coriolis and centripetal force vector and $G(q)\in\mathbb{R}^{12}$ is the gravitational force vector. The detailed kinematic and dynamic parameters can be found in the online source \cite{ourrobot}. For biped robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is planned in the joint space. Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to plan a stable walking pattern to prevent robot from falling. These make the motion planning of walking behavior of robot more difficult. In this paper, a Three-Dimensional Linear Inverted Pendulum Model (3D-LIPM) \cite{kajita2001real} is used for the motion planning of walking behavior of each biped robot in URTS.

@@

\textit{
    \begin{remark}
        A frame (or homogeneous transformation) in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame. That is, given the frames of two joints in links with known kinematics, the frames of joints between them can be found by \textnormal{IK}. Hence, we need to find the position path and orientation path, which compose the desired path of the frame.
    \end{remark}
}

@@

To plan the CoM postion path $(CP_n)$, ZMP path needs to be planned first. ZMP path can be planned through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path points out when the feet are on the ground. Suppose the CoM height $z_c$ of biped robot is kept constant when walking, then the biped robot model can be regarded as an 3D-LIPM \cite{kajita2001real}:
\begin{equation} \label{eq:LIPM}
    \begin{split}
        & \ddot{x}_c = \frac{g}{z_c}(x_c - p_x) \\
        & \ddot{y}_c = \frac{g}{z_c}(y_c - p_y)
    \end{split}
\end{equation}
where $(x_c, y_c, z_c)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, and $(p_x,p_y)$ is the position of ZMP on the $x$-$y$ plane. Since $z_c$, $g$ and $(p_x,p_y)$ are given, $(x_c, y_c)$ can be solved. From the dynamic equations in the $x$ and $y$ directions in (\ref{eq:LIPM}), it can be found that they are decoupled and thus can be calculated separately. Therefore, only the solution in the $x$ direction is given below (the $y$ direction as the same). To solve it, a method is proposed to convert it to a servo problem \cite{1241826}:
\begin{equation} \label{eq:output tracking}
    \begin{split}
        & \dot{\bar{x}}_c = A\bar{x}_c + Bu_s \\
        & y_s = C\bar{x}_c
    \end{split}
\end{equation}
where $\bar{x}_c = \begin{bmatrix}
    x_c \\ \dot{x}_c \\ \ddot{x}_c
\end{bmatrix}$, $A = \begin{bmatrix}
    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
\end{bmatrix}$, $B = \begin{bmatrix}
    0 \\ 0 \\ 1
\end{bmatrix}$, and $C = \begin{bmatrix}
    1 & 0 & -z_c/g
\end{bmatrix}$. Our goal is to find a control input $u_s$ in order that the output $y_s$ can track the ZMP reference trajectory $p_x$ so that the state $x_c$, i.e., the solution of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path can be planned. Unlike conventional methods, the problem is solved by the optimal control. The system is discretized first and the discrete LQ optimal tracker is employed to achieve the output tracking. The formulation of the discrete LQ optimal tracker can be found in TABLE 4.4-1 in \cite{lewis2012optimal}. The CoM position path $(CP_n)$ can then be obtained by combining $x_c$ and $y_c$ with $z_c$.

@@

\section{Reference tracking control of each agent in hybrid URTS}
Through the previous step, the planning of the reference path $r[k]$ of each agent in hybrid URTS has been completed. However, in order to calculate the unplannable reference paths, i.e., $\phi_r[k]$ and $\theta_r[k]$, of UAV and analyze the reference trajectory tracking problem in the continuous domain, we have to transform $r[k]$ into the reference trajectory $r(t)$. Before converting the planned reference path $r[k]$ to desired reference trajectory $r(t)$, we first convert the UAV dynamic model in (\ref{eq:uav}) and robot dynamic model in (\ref{eq:robot}) into a form called agent dynamic model in a hybrid team to analyze their team formation tracking control problems together. Through some appropriate variable transformations, we have:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
\end{equation}
where $u(t)\in\mathbb{R}^n$ is the control input vector, $x(t)\in\mathbb{R}^n$ is the state vector, $M(x(t))\in\mathbb{R}^{n\times n}$ is the inertia matrix, and $H(x(t),\dot{x}(t))\in\mathbb{R}^n$ is the non-inertial force vector. The control law for an agent in URTS is given as:
\begin{equation} \label{eq:control}
    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
\end{equation}
where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t))$, $\ddot{r}(t)$ and $H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system tracking robustness. For each UAV in hybrid URTS, we have $u(t)=\begin{bmatrix}
    f_u \\ \tau_u
\end{bmatrix}$, $x(t)=\begin{bmatrix}
    X \\ \Theta
\end{bmatrix}$, $M(x(t))=\begin{bmatrix}
    mI & 0 \\ 0 & J
\end{bmatrix}$, $H(x(t),\dot{x}(t))=\begin{bmatrix}
    0 \\ \dot{\Theta}\times(J\dot{\Theta})
\end{bmatrix}+\begin{bmatrix}
    f_g \\ 0
\end{bmatrix}+\begin{bmatrix}
    K_F & 0 \\
    0 & K_\tau
\end{bmatrix}\begin{bmatrix}
    \dot{X} \\ \dot{\Theta}
\end{bmatrix}$, and $n=6$ by UAV dynamics in (\ref{eq:uav}). For each robot in hybrid URTS, we have $u(t)=\tau_R$, $x(t)=q$, $M(x(t))=M_R(q)$, $H(x(t),\dot{x}(t))=C(q,\dot{q})\dot{q} + G(q)$, and $n=12$ by robot dynamics in (\ref{eq:robot}).
        In Section 3.2.2 of \cite{sabatino2015quadrotor}, the dynamic system of UAV is divided into inner loop system and outer loop system to analyze the reference tracking problem of UAV. In order to improve the problem that the control gains in four state equations ($z$, $\phi$, $\theta$ and $\psi$) of inner loop system and the two states of outer loop system ($x$ and $y$) in \cite{sabatino2015quadrotor} has no design specifications, we changed the controller design method so that the control gains of the six states of UAV can be designed together via the given specifications, i.e., design control law $u(t)\in\mathbb{R}^6$ to achieve the observer-based tracking specification in (\ref{Hinf}). This can reduce the time cost of manually adjusting control gains. At the same time, the tracking control problem of UAV and robot can be analyzed simultaneously.
        The difference between the control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedforward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$. This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be used in control law $u(t)$. While the asymptotical tracking control is achieved, i.e., $x(t)\rightarrow r(t)$, feedforward linearization control will be achieved too.
To complete the planning of reference trajectory $r(t)$ of each agent, a D/A converter is used to transform the reference path $r[k]$ (output of local motion planning) into a continuous signal $r'(t)$ as shown in Fig. \ref{fig:tracking}. For UAV, we get $r'(t) = [x_r, y_r, z_r, \phi_r]^T\in\mathbb{R}^{4}$. Besides, for an UAV in hybrid URTS, it can be seen that the control input $u(t)=[f_u^T, \tau_u^T]^T = [f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actuator control input $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ for UAV since UAV is an underactuated system. The two degrees of freedom we reserved in Section III-A, i.e., $\phi_r$ and $\theta_r$, are just to solve this problem. By substituting $\Theta=\begin{bmatrix}
    \phi_r \\ \theta_r \\ \psi_r
\end{bmatrix}$ into $\begin{bmatrix}
        f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
        0 \\ 0 \\ F
\end{bmatrix}$ from UAV dynacmis in (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations using inverse dynamic because the component forces $f_x$, $f_y$ and $f_z$, and the yaw angle $\psi_r$ are given. Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]^T$. At the same time, we find $u'(t)$. For biped robot, we directly have $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system. So far, the transformation from reference path $r[k]$ to reference trajectory $r(t)$ for each agent in hybrid URTS is done. We define the process of converting $r'(t)$ and $u(t)$ into $r(t)$ and $u'(t)$ mentioned above as the reference generation block in Fig. \ref{fig:tracking}.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/tracking.png}\caption{
    (a) The flowchart of Reference Tracking Control block in Fig. \ref{fig:sys} of each agent in hybrid URTS. The controller block is described in (d). The controller block (the proposed general $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system. It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actuator control input $u'(t)\in\mathbb{R}^4$ different for UAV. The reference generator block is introduced to deal with this problem. For UAVs, the reference generator block is described in (b). For robots, the reference generator block is described in (c). 
    (b) The reference generator block for each UAV. $u'(t)$ and $r(t)$ can be calculated from $u(t)$ and $r'(t)$ by inverse dynamic through the UAV dynamic model in (\ref{eq:uav}). 
    (c) The reference generator block for each robot. $u'(t)=u(t)$ and $r(t)=r'(t)$ since the robot dynamic model in (\ref{eq:robot}) is fully actuated. 
    (d) The proposed general $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme for each agent in hybrid URTS.}
    \label{fig:tracking}
\end{figure*}

\textit{
    \begin{remark}
        Since this article analyzes each agent $\alpha_{i,j}$ individually, the subscripts $i$ and $j$ of the corresponding variables are omitted for the convenience of notation in the following. For example, $x_{i,j}(t)$ is omitted as $x(t)$ in (\ref{eq:agent}), $r_{i,j}(t)$ is omitted as $r(t)$ in (\ref{eq:control}), etc.
    \end{remark}
}
\textit{
    \begin{remark}
        Let $r_{i,j}(t)$ be the reference trajectory $r(t)$ of the agent $\alpha_{i,j}$, $r_{i,j}[k]$ be the reference path $r[k]$ of the agent $\alpha_{i,j}$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$ of the agent $\alpha_{i,j}$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$ of the agent $\alpha_{i,j}$, $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$, etc. As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, Task Allocation, Global Path Planning, Behavior Decision and Local Motion Planning, have completed their respective responsibilities and planned their corresponding values, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$. That is, $r_{i,j}(t)$ is the reference trajectory that can accomplish the specific task, follow the specific path and perform the specific behavior.
    \end{remark}
}
